The Weakly Nonlinear Magnetorotational Instability in a Global, Cylindrical Taylor-Couette Flow

### 2017-03-13 paper/widegap_ref_response/widegap_mri_paper_ref_response_apj.tex
many more additions to text
for numerical convergence plot
replaced beta with Co in widegap paper too

\begin{table*}[ht]
\normalsize
\caption{Fiducial parameters for MRI runs} \label{table:parameters}
\centering
\begin{tabular}{rlrrrrrrr}
  \hline
 & $\xi$ & $\Pm$ & $\beta$ & $\Omega_2/\Omega_1$ & $R_1/R_2$ & radial magnetic b.c. \\ 
  \hline\hline
Standard MRI & 0 & 1.6E-6 & 41.2 & 0.121 & 0.33 & conducting \\ 
Helical MRI & 4 & 1E-6 & 1.7E-2 & 0.27 & 0.5 & insulating\\ 
   \hline
\end{tabular}
\end{table*}

@@

\begin{figure*}
\centering
%\includegraphics[width=\textwidth]{widegap_orders1_2_Pm16E-7}
\caption{Eigenfunctions of the first order equations, first order adjoint homogenous equations, and second order equations. We use our fiducial parameters for the standard MRI ($\xi = 0$). Eigenfunctions are solved on a 512-element grid of Chebyshev polynomials. First-order eigenfunctions are normalized such that $A_{11}(r_0) = 1$. Adjoint homogenous eigenfunctions are normalized such that $\langle V_{11}^\dagger \cdot \mathcal{D} V_{11} \rangle = 1$.}\label{fig:linear_eigenfunctions}
\end{figure*}

@@

\begin{figure*}
\centering
%\includegraphics[width=\textwidth]{widegap_n2_n3_Pm16E-7.pdf}
\caption{Nonlinear terms $N_2$ and $N_3$ for our fiducial standard MRI parameters. These are nonlinear combinations of lower-order eigenfunctions. At second order ($N_2$) the most unstable linear MRI mode interacts with itself and its complex conjugate. At third order ($N_3$) the first and second order MRI modes interact with each other.}\label{fig:N2_N3}
\end{figure*}

@@

Our perturbed system is 
\onecolumngrid
\beq\label{eq:Psi_perturbed}
\frac{1}{r}\partial_t (\nabla^2 \Psi - \frac{2}{r} \partial_r \Psi) - \frac{2}{\beta} \frac{1}{r}B_0 \partial_z (\nabla^2 A - \frac{2}{r} \partial_r A) - \frac{2}{r}u_0 \partial_z u_\phi + \frac{2}{\beta} \frac{2}{r^2}B_0 \xi \partial_z B_\phi - \frac{1}{\reye} \left[ \nabla^2 (\frac{1}{r} \nabla^2 \Psi - \frac{2}{r^2}\partial_r\Psi) - \frac{1}{r^3} \nabla^2 \Psi + \frac{2}{r^4}\partial_r\Psi\right] = N^{(\Psi)}
\eeq

\beq \label{eq:uphi_perturbed}
\partial_t \uphi + \frac{1}{r^2} u_0 \partial_z \Psi + \frac{1}{r} \partial_r u_0 \partial_z \Psi - \frac{2}{\beta} B_0 \partial_z B_\phi - \frac{1}{\reye} ( \nabla^2 \uphi - \frac{1}{r^2} \uphi ) = N^{(u)}
\eeq

@@

\beq
N^{(\Psi)} = - J(\Psi, \frac{1}{r^2} ( \nabla^2 \Psi - \frac{2}{r} \partial_r\Psi) ) + \frac{2}{\beta} J(A, \frac{1}{r^2} ( \nabla^2 A - \frac{2}{r} \partial_rA) ) - \frac{2}{\beta} \frac{2}{r}B_\phi \partial_z B_\phi  + \frac{2}{r} u_\phi \partial_z u_\phi 
\eeq
\beq
N^{(u)} = \frac{2}{\beta} \frac{1}{r} J(A, B_\phi) - \frac{1}{r} J(\Psi, \uphi) + \frac{2}{\beta}\frac{1}{r^2} B_\phi \partial_z A - \frac{1}{r^2} \uphi \partial_z \Psi 
\eeq
\beq
N^{(A)} = \frac{1}{r} J(A, \psi)
\eeq
\beq
N^{(B)} = \frac{1}{r} J(A, \uphi) + \frac{1}{r} J(B_\phi, \psi) + \frac{1}{r^2} B_\phi \partial_z \psi - \frac{1}{r^2} \uphi \partial_z A 
\label{eq:nonlinear_B}
\eeq
\twocolumngrid

where J is the Jacobian $J(f, g) \equiv \partial_z f \partial_r g - \partial_r f \partial_z g$. Note that in the above, $\nabla^2 f \equiv \partial_r^2 f + \partial_z^2 f + \frac{1}{r} \partial_r f$. Equations \ref{eq:Psi_perturbed} - \ref{eq:nonlinear_B} are nondimensionalized by inner cylinder quantities: lengths have been scaled by $r_1$, velocities by $r_1 \Omega_1$, and densities by $\rho_0$, where $\rho_0$ is the constant density. Magnetic fields are scaled by $B_0$, the constant strength of the initial background field; where $B_0$ appears in the above it is formally unity. $\Omega_1 = \Omega(r_1)$ is the rotation rate of the inner cylinder. We introduce the Reynolds number $\reye = \Omega_1 r_1^2/\nu$, the magnetic Reynolds number $\reym = \Omega_1 r_1^2 / \eta$, and a plasma beta parameter $\beta = \Omega_1^2 r_1^2 \rho_0/B_0^2$. Note that if we define the dimensional cylindrical coordinate $r = r_1(1 + \delta x)$, we recover the narrow gap approximation of the system in the limit $\delta \rightarrow 0$.

@@

We find the marginal system as a function of the dimensionless parameters. The marginal stability curve for our standard MRI system is a hyperplane in $(\reym, \Pm, \beta, \Omega_2/\Omega_1, \mathrm{R}_1/\mathrm{R}_2$), but we hold all of these constant except for $\reym$. To analyze the MRI system at marginality, we fix the parameters listed in Table \ref{table:parameters} and determine the critical $\reym$ and vertical wavenumber $k_z$ by repeatedly solving the linear MRI system to determine the smallest parameter values for which the fastest growing mode has zero growth rate. That is, we solve the linear eigenvalue problem for eigenvalues $\sigma = \gamma + i \omega$ and determine the parameters which yield $\gamma = 0$. Figure \ref{fig:growth_rates} shows linear MRI growth rates $\gamma$ in the $(\reym, k_z)$ plane. For the fiducial standard MRI parameters in Table \ref{table:parameters} we find critical parameters $\reym_c = 3.30$ and $k_c = 0.901$.

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{widegap_totalstress_intstress-eps-converted-to.pdf}
\caption{Total stress $\mathrm{T}(r, z) = u_r u_\phi - \frac{2}{\beta} B_r B_\phi$, i.e. the sum of the Reynolds and Maxwell stresses for the fiducial standard MRI parameters (top panel). Bottom panel shows the vertically integrated stress $\int \mathrm{T}(r, z) \, dz$.}\label{fig:total_stress}
\end{figure}

@@

\section{A. Detailed Equations}\label{app:basic_equations}

@@

\beq
\mathcal{L}_1 = \left[\begin{matrix}
0 & -\frac{2}{r} u_0 & \frac{2}{\beta} (\frac{1}{r^2} \partial_r - \frac{1}{r}\partial_r^2) & 0 \\
\frac{1}{r^2} u_0 + \frac{1}{r}\partial_r u_0 & 0 & 0 & -\frac{2}{\beta} \\
-1 & 0 & 0 & 0 \\
0 & -1 & \frac{1}{r^2} u_0 - \frac{1}{r} \partial_r u_0 & 0 \\
\end{matrix}\right]
\eeq

@@

\beq
\mathcal{L}_3 = \left[\begin{matrix}
0 & 0 & -\frac{2}{\beta}\frac{1}{r} & 0 \\
0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 \\
\end{matrix}\right]
\eeq

@@

\beq
\mathcal{G} = \left[\begin{matrix}
0 & 0 & \frac{2}{\beta}(\frac{1}{r^2}\partial_r - \frac{1}{r}\partial_r^2) & 0 \\
0 & 0 & 0 & -\frac{2}{\beta} \\
-1 & 0 & 0 & 0 \\
0 & -1 & 0 & 0 \\
\end{matrix}\right]
\eeq

\beq
\mathcal{H} = \left[\begin{matrix}
0 & 0 & 0 & \frac{2}{\beta} \frac{2}{r^2} \\
0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 \\
-\frac{2}{r^3} & 0 & 0 & 0 \\
\end{matrix}\right]
\eeq

@@

\beq
\mathcal{L}_1^\dagger = \left[\begin{matrix}
0 & \frac{1}{r^2} u_0 + \frac{1}{r}\partial_r u_0 & -1 & 0 \\
-\frac{2}{r}u_0 & 0 & 0 & -1 \\
\frac{2}{\beta}(\frac{1}{r^3} - \frac{1}{r^2}\partial_r - \frac{1}{r}\partial_r^2) & 0 & 0 & \frac{1}{r^2}u_0 - \frac{1}{r}\partial_r u_0 \\
0 & -\frac{2}{\beta} & 0 & 0 \\
\end{matrix}\right],
\eeq

@@

%%%%% NONLINEAR TERMS %%%%%%%%%%%
\section{B. Nonlinear Terms}\label{app:nonlinear_terms}

@@

\beq
N_2^{\Psi}  = -J(\Psi_1, \frac{1}{r^2} \nabla^2 \Psi_1) - J(\Psi_1, -\frac{2}{r^3}\partial_r\Psi_1)
+ \frac{2}{\beta} J (A_1, \frac{1}{r^2} \nabla^2 A_1) + \frac{2}{\beta} J(A_1, -\frac{2}{r^3} \partial_r A_1) + \frac{2}{r} u_1 \partial_z u_1 - \frac{2}{\beta} \frac{2}{r} B_1 \partial_z B_1
\eeq

\beq
\begin{split}
N_2^{u} = -\frac{1}{r} J\left(\Psi_1, u_1\right) + \frac{1}{r} \frac{2}{\beta} J\left(A_1, B_1\right) - \frac{1}{r^2} u_1 \partial_z \Psi_1 + \frac{2}{\beta}\frac{1}{r^2} B_1 \partial_z A_1
\end{split}
\eeq

@@

\beq
\begin{split}
N_3^{\Psi} & = -J(\Psi_1, \frac{1}{r^2} \nabla^2 \Psi_2) - J(\Psi_2, \frac{1}{r^2} \nabla^2\Psi_1) - 2 J (\Psi_1, \frac{1}{r^2}\partial_Z\partial_z \Psi_1) - J(\Psi_1, -\frac{2}{r^3}\partial_r \Psi_2) - J(\Psi_2, -\frac{2}{r^3}\partial_r \Psi_1) \\
& - \widetilde{J}(\Psi_1, \frac{1}{r^2} \nabla^2 \Psi_1) - \widetilde{J} (\Psi_1, -\frac{2}{r^3}\partial_r \Psi_1) + \frac{2}{\beta} J(A_1, \frac{1}{r^2}\nabla^2 A_2) + \frac{2}{\beta} J(A_2, \frac{1}{r^2}\nabla^2 A_1) + \frac{4}{\beta} J(A_1, \frac{1}{r^2}\partial_Z\partial_z A_1) \\ 
& + \frac{2}{\beta} J(A_1, -\frac{2}{r^3} \partial_r A_2 ) + \frac{2}{\beta} J(A_2, -\frac{2}{r^3} \partial_r A_1) + \frac{2}{\beta} \widetilde{J} (A_1, \frac{1}{r^2} \nabla^2 A_1) + \frac{2}{\beta} \widetilde{J} (A_1, -\frac{2}{r^3} \partial_r A_1) \\
& + \frac{2}{r} u_1 \partial_z u_2 + \frac{2}{r} u_2 \partial_z u_1 + \frac{2}{r} u_1 \partial_Z u_1 - \frac{2}{\beta}\frac{2}{r} B_1\partial_z B_2 - \frac{2}{\beta}\frac{2}{r} B_2 \partial_z B_1 - \frac{2}{\beta} \frac{2}{r} B_1 \partial_Z B_1
\end{split}
\eeq

\beq
\begin{split}
N_3^u & = -\frac{1}{r}J\left(\Psi_1, u_2\right) - \frac{1}{r}J\left(\Psi_2, u_1\right) - \frac{1}{r}\widetilde{J} \left(\Psi_1, u_1\right) + \frac{1}{r}\frac{2}{\beta} J\left(A_1, B_2\right) + \frac{1}{r} \frac{2}{\beta} J\left(A_2, B_1\right) + \frac{1}{r}\frac{2}{\beta}\widetilde{J}\left(A_1, B_1\right) \\
& - \frac{1}{r^2} u_1\partial_z \Psi_2 - \frac{1}{r^2} u_2 \partial_z \Psi_1 - \frac{1}{r^2} u_1 \partial_Z \Psi_1 + \frac{2}{\beta} \frac{1}{r^2} B_1 \partial_z A_2 + \frac{2}{\beta} \frac{1}{r^2} B_2 \partial_z A_1 + \frac{2}{\beta} \frac{1}{r^2} B_1 \partial_Z A_1
\end{split}
\eeq

>>>>

\begin{table*}[ht]
\normalsize
\caption{Fiducial parameters for MRI runs} \label{table:parameters}
\centering
\begin{tabular}{rlrrrrrrr}
  \hline
 & $\xi$ & $\Pm$ & $\Co$ & $\Omega_2/\Omega_1$ & $R_1/R_2$ & radial magnetic b.c. \\ 
  \hline\hline
%Standard MRI & 0 & 1.6E-6 & 41.2 & 0.121 & 0.33 & conducting \\ 
Standard MRI & 0 & 1.6E-6 & 4.85E-2 & 0.121 & 0.33 & conducting \\ 
Helical MRI & 4 & 1E-6 & 118 & 0.27 & 0.5 & insulating\\ 
   \hline
\end{tabular}
\end{table*}

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{widegap_orders1_2_Pm16E-7}
\caption{Eigenfunctions of the first order equations, first order adjoint homogenous equations, and second order equations. We use our fiducial parameters for the standard MRI ($\xi = 0$). Eigenfunctions are solved on a 512-element grid of Chebyshev polynomials. First-order eigenfunctions are normalized such that $A_{11}(r_0) = 1$. Adjoint homogenous eigenfunctions are normalized such that $\langle V_{11}^\dagger \cdot \mathcal{D} V_{11} \rangle = 1$.}\label{fig:linear_eigenfunctions}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{widegap_n2_n3_Pm16E-7.pdf}
\caption{Nonlinear terms $N_2$ and $N_3$ for our fiducial standard MRI parameters. These are nonlinear combinations of lower-order eigenfunctions. At second order ($N_2$) the most unstable linear MRI mode interacts with itself and its complex conjugate. At third order ($N_3$) the first and second order MRI modes interact with each other.}\label{fig:N2_N3}
\end{figure*}

@@

Our perturbed system is 
\onecolumngrid
\beq\label{eq:Psi_perturbed}
\frac{1}{r}\partial_t (\nabla^2 \Psi - \frac{2}{r} \partial_r \Psi) - \Co \frac{1}{r}B_0 \partial_z (\nabla^2 A - \frac{2}{r} \partial_r A) - \frac{2}{r}u_0 \partial_z u_\phi + \Co \frac{2}{r^2}B_0 \xi \partial_z B_\phi - \frac{1}{\reye} \left[ \nabla^2 (\frac{1}{r} \nabla^2 \Psi - \frac{2}{r^2}\partial_r\Psi) - \frac{1}{r^3} \nabla^2 \Psi + \frac{2}{r^4}\partial_r\Psi\right] = N^{(\Psi)}
\eeq

\beq \label{eq:uphi_perturbed}
\partial_t \uphi + \frac{1}{r^2} u_0 \partial_z \Psi + \frac{1}{r} \partial_r u_0 \partial_z \Psi - \Co B_0 \partial_z B_\phi - \frac{1}{\reye} ( \nabla^2 \uphi - \frac{1}{r^2} \uphi ) = N^{(u)}
\eeq

@@

\beq
N^{(\Psi)} = - J(\Psi, \frac{1}{r^2} ( \nabla^2 \Psi - \frac{2}{r} \partial_r\Psi) ) + \Co J(A, \frac{1}{r^2} ( \nabla^2 A - \frac{2}{r} \partial_rA) ) - \Co \frac{2}{r}B_\phi \partial_z B_\phi  + \frac{2}{r} u_\phi \partial_z u_\phi 
\eeq
\beq
N^{(u)} = \Co \frac{1}{r} J(A, B_\phi) - \frac{1}{r} J(\Psi, \uphi) + \Co \frac{1}{r^2} B_\phi \partial_z A - \frac{1}{r^2} \uphi \partial_z \Psi 
\eeq
\beq
N^{(A)} = \frac{1}{r} J(A, \psi)
\eeq
\beq
N^{(B)} = \frac{1}{r} J(A, \uphi) + \frac{1}{r} J(B_\phi, \psi) + \frac{1}{r^2} B_\phi \partial_z \psi - \frac{1}{r^2} \uphi \partial_z A 
\label{eq:nonlinear_B}
\eeq
\twocolumngrid

where J is the Jacobian $J(f, g) \equiv \partial_z f \partial_r g - \partial_r f \partial_z g$. Note that in the above, $\nabla^2 f \equiv \partial_r^2 f + \partial_z^2 f + \frac{1}{r} \partial_r f$. Equations \ref{eq:Psi_perturbed} - \ref{eq:nonlinear_B} are nondimensionalized by inner cylinder quantities: lengths have been scaled by $r_1$, velocities by $r_1 \Omega_1$, and densities by $\rho_0$, where $\rho_0$ is the constant density. Magnetic fields are scaled by $B_0$, the constant strength of the initial background field; where $B_0$ appears in the above it is formally unity. $\Omega_1 = \Omega(r_1)$ is the rotation rate of the inner cylinder. We introduce the Reynolds number $\reye = \Omega_1 r_1^2/\nu$, the magnetic Reynolds number $\reym = \Omega_1 r_1^2 / \eta$, and a plasma beta parameter $\Co = 2 B_0^2 / \Omega_1^2 r_1^2 \rho_0$. %$\beta = \Omega_1^2 r_1^2 \rho_0/B_0^2$. 
Note that if we define the dimensional cylindrical coordinate $r = r_1(1 + \delta x)$, we recover the narrow gap approximation of the system in the limit $\delta \rightarrow 0$.

@@

We find the marginal system as a function of the dimensionless parameters. The marginal stability curve for our standard MRI system is a hyperplane in $(\reym, \Pm, \Co, \Omega_2/\Omega_1, \mathrm{R}_1/\mathrm{R}_2$), but we hold all of these constant except for $\reym$. To analyze the MRI system at marginality, we fix the parameters listed in Table \ref{table:parameters} and determine the critical $\reym$ and vertical wavenumber $k_z$ by repeatedly solving the linear MRI system to determine the smallest parameter values for which the fastest growing mode has zero growth rate. That is, we solve the linear eigenvalue problem for eigenvalues $\sigma = \gamma + i \omega$ and determine the parameters which yield $\gamma = 0$. Figure \ref{fig:growth_rates} shows linear MRI growth rates $\gamma$ in the $(\reym, k_z)$ plane. For the fiducial standard MRI parameters in Table \ref{table:parameters} we find critical parameters $\reym_c = 3.30$ and $k_c = 0.901$.

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{widegap_totalstress_intstress-eps-converted-to.pdf}
\caption{Total stress $\mathrm{T}(r, z) = u_r u_\phi - \Co B_r B_\phi$, i.e. the sum of the Reynolds and Maxwell stresses for the fiducial standard MRI parameters (top panel). Bottom panel shows the vertically integrated stress $\int \mathrm{T}(r, z) \, dz$.}\label{fig:total_stress}
\end{figure}

@@

\section{Detailed Equations}\label{app:basic_equations}

@@

\beq
\mathcal{L}_1 = \left[\begin{matrix}
0 & -\frac{2}{r} u_0 & \Co (\frac{1}{r^2} \partial_r - \frac{1}{r}\partial_r^2) & 0 \\
\frac{1}{r^2} u_0 + \frac{1}{r}\partial_r u_0 & 0 & 0 & -\Co \\
-1 & 0 & 0 & 0 \\
0 & -1 & \frac{1}{r^2} u_0 - \frac{1}{r} \partial_r u_0 & 0 \\
\end{matrix}\right]
\eeq

@@

\beq
\mathcal{L}_3 = \left[\begin{matrix}
0 & 0 & -\Co \frac{1}{r} & 0 \\
0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 \\
\end{matrix}\right]
\eeq

@@

\beq
\mathcal{G} = \left[\begin{matrix}
0 & 0 & \Co (\frac{1}{r^2}\partial_r - \frac{1}{r}\partial_r^2) & 0 \\
0 & 0 & 0 & -\Co \\
-1 & 0 & 0 & 0 \\
0 & -1 & 0 & 0 \\
\end{matrix}\right]
\eeq

\beq
\mathcal{H} = \left[\begin{matrix}
0 & 0 & 0 & \Co \frac{2}{r^2} \\
0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 \\
-\frac{2}{r^3} & 0 & 0 & 0 \\
\end{matrix}\right]
\eeq

@@

\beq
\mathcal{L}_1^\dagger = \left[\begin{matrix}
0 & \frac{1}{r^2} u_0 + \frac{1}{r}\partial_r u_0 & -1 & 0 \\
-\frac{2}{r}u_0 & 0 & 0 & -1 \\
\Co (\frac{1}{r^3} - \frac{1}{r^2}\partial_r - \frac{1}{r}\partial_r^2) & 0 & 0 & \frac{1}{r^2}u_0 - \frac{1}{r}\partial_r u_0 \\
0 & -\Co & 0 & 0 \\
\end{matrix}\right],
\eeq

@@

%%%%% NONLINEAR TERMS %%%%%%%%%%%
\section{Nonlinear Terms}\label{app:nonlinear_terms}

@@

\beq
N_2^{\Psi}  = -J(\Psi_1, \frac{1}{r^2} \nabla^2 \Psi_1) - J(\Psi_1, -\frac{2}{r^3}\partial_r\Psi_1)
+ \Co J (A_1, \frac{1}{r^2} \nabla^2 A_1) + \Co J(A_1, -\frac{2}{r^3} \partial_r A_1) + \frac{2}{r} u_1 \partial_z u_1 - \Co \frac{2}{r} B_1 \partial_z B_1
\eeq

\beq
\begin{split}
N_2^{u} = -\frac{1}{r} J\left(\Psi_1, u_1\right) + \frac{1}{r} \Co J\left(A_1, B_1\right) - \frac{1}{r^2} u_1 \partial_z \Psi_1 + \Co \frac{1}{r^2} B_1 \partial_z A_1
\end{split}
\eeq

@@

\beq
\begin{split}
N_3^{\Psi} & = -J(\Psi_1, \frac{1}{r^2} \nabla^2 \Psi_2) - J(\Psi_2, \frac{1}{r^2} \nabla^2\Psi_1) - 2 J (\Psi_1, \frac{1}{r^2}\partial_Z\partial_z \Psi_1) - J(\Psi_1, -\frac{2}{r^3}\partial_r \Psi_2) - J(\Psi_2, -\frac{2}{r^3}\partial_r \Psi_1) \\
& - \widetilde{J}(\Psi_1, \frac{1}{r^2} \nabla^2 \Psi_1) - \widetilde{J} (\Psi_1, -\frac{2}{r^3}\partial_r \Psi_1) + \Co J(A_1, \frac{1}{r^2}\nabla^2 A_2) + \Co J(A_2, \frac{1}{r^2}\nabla^2 A_1) + 2\Co J(A_1, \frac{1}{r^2}\partial_Z\partial_z A_1) \\ 
& + \Co J(A_1, -\frac{2}{r^3} \partial_r A_2 ) + \Co J(A_2, -\frac{2}{r^3} \partial_r A_1) + \Co \widetilde{J} (A_1, \frac{1}{r^2} \nabla^2 A_1) + \Co \widetilde{J} (A_1, -\frac{2}{r^3} \partial_r A_1) \\
& + \frac{2}{r} u_1 \partial_z u_2 + \frac{2}{r} u_2 \partial_z u_1 + \frac{2}{r} u_1 \partial_Z u_1 - \Co \frac{2}{r} B_1\partial_z B_2 - \Co \frac{2}{r} B_2 \partial_z B_1 - \Co \frac{2}{r} B_1 \partial_Z B_1
\end{split}
\eeq

\beq
\begin{split}
N_3^u & = -\frac{1}{r}J\left(\Psi_1, u_2\right) - \frac{1}{r}J\left(\Psi_2, u_1\right) - \frac{1}{r}\widetilde{J} \left(\Psi_1, u_1\right) + \frac{1}{r}\Co J\left(A_1, B_2\right) + \frac{1}{r} \Co J\left(A_2, B_1\right) + \frac{1}{r}\Co \widetilde{J}\left(A_1, B_1\right) \\
& - \frac{1}{r^2} u_1\partial_z \Psi_2 - \frac{1}{r^2} u_2 \partial_z \Psi_1 - \frac{1}{r^2} u_1 \partial_Z \Psi_1 + \Co \frac{1}{r^2} B_1 \partial_z A_2 + \Co \frac{1}{r^2} B_2 \partial_z A_1 + \Co \frac{1}{r^2} B_1 \partial_Z A_1
\end{split}
\eeq
